---
title: "KeyATM Report"
author: "Maksim Zubok"
date: "2024-02-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr, tidyverse, rio, ggplot2, lubridate, quanteda, keyATM, readxl, caret)

```

## Report


```{r cars}
load("outputs/keyatm_env.RData")

```

## Pro-Regime Automated vs Manual

Correspondence between automated and manual labels measured by accuracy is 0.66.


```{r echo=FALSE}
# Convert the summarized data to a Markdown table
markdown_table <- kable(conf_matrix_regime$overall, format = "markdown", digits = 2)

# Print the Markdown table
markdown_table
```

The corresponding confusion matrix: 

```{r echo=FALSE}
# Convert the summarized data to a Markdown table
markdown_table <- kable(conf_matrix_regime$table, format = "markdown")

# Print the Markdown table
markdown_table
```


## Protest KeyATM Automated vs Manual

Correspondence between automated and manual labels as by accuracy is 0.64.


```{r echo=FALSE}
# Convert the summarized data to a Markdown table
markdown_table <- kable(conf_matrix_protest_type$overall, format = "markdown", digits = 2)

# Print the Markdown table
markdown_table
```


The aggregate performance averages out great performance on some categories (war, environment, legal), at best average performance on other classes (economic and political) and poor performance on the rest (cultural, social). 

```{r echo=FALSE}
# Convert the summarized data to a Markdown table
df = data.frame(conf_matrix_protest_type$byClass) %>% 
  select(-c("Neg.Pred.Value", "Pos.Pred.Value", 
            "Prevalence" ,"Detection.Prevalence" ,"Detection.Prevalence"))
markdown_table <- kable(df, format = "markdown", digits = 2)

# Print the Markdown table
markdown_table
```


The corresponding Confusion matrix for KeyATM protest types. 

```{r echo=FALSE}
# Convert the summarized data to a Markdown table
markdown_table <- kable(conf_matrix_protest_type$table, format = "markdown")

# Print the Markdown table
markdown_table
```


## Visualisations 

matching Madelene's plots 

```{r echo=FALSE}
acled_with_preds <- acled_with_preds %>% 
  mutate(date = dmy(event_date),
         month_year = format(date, "%Y-%m"))
```



```{r echo=FALSE}
unique_counts_polit <- acled_with_preds %>%
  mutate(month_year = as.Date(paste0(month_year, "-01"))) %>%
  group_by(month_year, protest_type) %>%
  summarise(unique_notes = n_distinct(notes))


# Plotting
political_protests_plot <- ggplot(unique_counts_polit, aes(x = month_year, y = unique_notes, color = protest_type)) +
  geom_line() +
  geom_point() +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y", minor_breaks = "1 month") +
  labs(title = "Monthly Number of Unique Protests in Russia",
       x = "",
       y = "Number of Unique Protests",
       linetype = "") +  # Set legend title to no title
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_vline(xintercept = as.Date("2022-02-24"), linetype = "dashed", color = "red")


political_protests_plot
```

```{r echo=FALSE}
# Calculating the share of each protest type per month
unique_counts_polit <- acled_with_preds %>%
  mutate(month_year = as.Date(paste0(month_year, "-01"))) %>%
  group_by(month_year, protest_type) %>%
  summarise(unique_notes = n_distinct(notes), .groups = 'drop') %>%
  # Calculate total protests per month across all types
  group_by(month_year) %>%
  mutate(total_notes = sum(unique_notes)) %>%
  # Calculate the share of protests for each type
  mutate(share_of_protests = unique_notes / total_notes) %>%
  # Select only necessary columns
  select(month_year, protest_type, share_of_protests)

# Plotting the shares
political_protests_plot <- ggplot(unique_counts_polit, aes(x = month_year, y = share_of_protests, color = protest_type)) +
  geom_line() +
  geom_point() +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y", minor_breaks = "1 month") +
  labs(title = "Monthly Share of Protests by Type in Russia",
       x = "",
       y = "Share of Total Protests",
       color = "Protest Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_vline(xintercept = as.Date("2022-02-24"), linetype = "dashed", color = "red")

# Display the plot
print(political_protests_plot)
```

