---
title: "March Survey Report"
author: "Maksim Zubok"
date: 
output: 
  pdf_document:
    latex_engine: lualatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

Sys.getlocale()
# Set this to a locale that supports Cyrillic, for example, on Windows
Sys.setlocale("LC_ALL", "Russian")

##### Set Up #####
pacman::p_load(tidyverse, readr, broom, 
               lubridate, gt, gtsummary, survey, readxl,
               gridExtra, knitr, haven)

# categories for education
uni_education <- c("Высшее образование (магистратура)",
                   "Высшее образование (бакалавриат / специалитет)",
                   "Научная степень (кандидат, доктор наук)")

# load levada data
levada_omnibus <- read_sav("data/surveys/levada_omnibus") %>% 
  mutate(gender = fct_recode(as.factor(qS1),
                          "Man"= "1",
                          "Woman" = "2"),
          #adjust age
          age_group = case_when(
            as.numeric(qS2) %in% c(18:24) ~ '18-24',
            as.numeric(qS2) %in% c(25:34) ~ '25-34',
            as.numeric(qS2) %in% c(35:44) ~ '35-44',
            as.numeric(qS2) %in% c(45:54) ~ '45-54',
            as.numeric(qS2) %in% c(55:64) ~ '55-64',
            as.numeric(qS2) >= 65 ~ '65+',
            TRUE ~ NA),
         university_education = case_when(qS3 == 6 ~ "BA+",
                                     TRUE ~ "BA-")
         )


# load survey data
survey_march <- read_csv("data/surveys/survey_march_post_election.csv",
                         locale = locale(encoding = "UTF-8")) %>% 
  mutate(gender = fct_recode(Q4,
                          "Man"= "Мужской",
                          "Woman" = "Женский"),
          #adjust age
          age_group = case_when(
            as.numeric(Q1) %in% c(18:24) ~ '18-24',
            as.numeric(Q1) %in% c(25:34) ~ '25-34',
            as.numeric(Q1) %in% c(35:44) ~ '35-44',
            as.numeric(Q1) %in% c(45:54) ~ '45-54',
            as.numeric(Q1) %in% c(55:64) ~ '55-64',
            as.numeric(Q1) >= 65 ~ '65+',
            TRUE ~ NA),
         university_education = case_when(Q5 %in% uni_education ~ "BA+",
                                     TRUE ~ "BA-")
         )

survey_feb <- read_xlsx("data/surveys/survey_feb.xlsx")[-1, ] %>% 
  mutate(gender = fct_recode(as.factor(Q4),
                          "Man"= "Мужской",
                          "Woman" = "Женский"),
          #adjust age
          age_group = case_when(
            as.numeric(Q1) %in% c(18:24) ~ '18-24',
            as.numeric(Q1) %in% c(25:34) ~ '25-34',
            as.numeric(Q1) %in% c(35:44) ~ '35-44',
            as.numeric(Q1) %in% c(45:54) ~ '45-54',
            as.numeric(Q1) %in% c(55:64) ~ '55-64',
            as.numeric(Q1) >= 65 ~ '65+',
            TRUE ~ NA),
         university_education = case_when(Q5 %in% uni_education ~ "BA+",
                                     TRUE ~ "BA-")
         )

survey_aug <- read_csv("data/surveys/survey_aug.csv",
                       locale = locale(encoding = "UTF-8")) %>% 
  # adjust education
  # education %in% na_education ~ "NA"
  filter(gender != "no_answer") %>% 
    mutate(university_education = case_when(
      education %in% uni_education ~ "BA+",
      TRUE ~ "BA-"),
      gender = fct_recode(gender,
                             "Man"= "Мужской",
                             "Woman" = "Женский"),
      university_education = case_when(education %in% uni_education ~ "BA+",
                                     TRUE ~ "BA-")
    )


# helper funcitons
calculate_shares <- function(dataset, dataset_name) {
  dataset %>%
    pivot_longer(cols = c(age_group, gender, university_education), names_to = "Variable", values_to = "Values") %>%
    group_by(Variable, Values) %>%
    summarise(Share = n() / nrow(dataset), .groups = 'drop') %>%
    mutate(Survey = dataset_name,
           Share = round(Share, 2))
}
```

## Sample Comparison against Levada Benchmark


Table 1 compares the demographic
composition of Qualtrics samples collected in August, February, and March to nationally representative Levada Omnibus survey.

```{r}
shares_levada <- calculate_shares(levada_omnibus, "Levada")
shares_survey_march <- calculate_shares(survey_march, "Q. March")
shares_survey_feb <- calculate_shares(survey_feb, "Q. February")
shares_survey_aug <- calculate_shares(survey_aug, "Q. August")


combined_shares <- bind_rows(shares_levada,
                             shares_survey_march,
                             shares_survey_feb,
                             shares_survey_aug) %>%
  pivot_wider(names_from = Survey, values_from = Share) %>% 
  mutate(Variable = case_when(
    Variable == "age_group" ~ "Age", # improve visibility
    Variable == "gender" ~ "Gender",
    Variable == "university_education" ~ "Education",
    TRUE ~ Variable # default case to leave the variable name as it is
  ))

kable(combined_shares, caption = "Comparison of Category Shares by Variable",
      align = "c",
      format = "markdown")

```
The only major difference between all Qualtrics surveys and Levada Omnibus is the shares of education categories, with the former having twice as high of a share of people with completed university education. 
