---
title: "February Survey Report"
author: "Maksim Zubok"
date: "2024-03-15"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


##### Set Up #####
pacman::p_load(tidyverse, readr, broom, 
               lubridate, gt, gtsummary, survey, readxl)


# load survey data
survey_feb <- read_xlsx("data/surveys/survey_feb.xlsx")
# clean data
column_descriptions <- as.character(unlist(survey_feb[1, ]))
names(column_descriptions) <- names(survey_feb)
# example, call: column_descriptions["Q1"]

# remove first row
survey_feb <- survey_feb[-1,]

# categories for education
uni_education <- c("Высшее образование (магистратура)",
                   "Высшее образование (бакалавриат / специалитет)",
                   "Научная степень (кандидат, доктор наук)")

na_education <- c("Затрудняюсь ответить", "Отказ от ответа", "no_answer")

survey_feb <- survey_feb %>%
  mutate(
    gender = as.factor(Q4),
    # adjust dates 
    StartDate = as.POSIXct((as.numeric(StartDate) - 25569) * 86400, origin = "1970-01-01", tz = "UTC"),
    EndDate = as.POSIXct((as.numeric(EndDate) - 25569) * 86400, origin = "1970-01-01", tz = "UTC"),
    RecordedDate = as.POSIXct((as.numeric(RecordedDate) - 25569) * 86400, origin = "1970-01-01", tz = "UTC"),
    # adjust education
    university_education = case_when(Q5 %in% uni_education ~ "BA+",
                                     Q5 %in% na_education ~ "NA",
                                     TRUE ~ "BA-"),
    #adjust age
    age_group = case_when(
      as.numeric(Q1) %in% c(18:19) ~ '18-19',
      as.numeric(Q1) %in% c(20:24) ~ '20-24',
      as.numeric(Q1) %in% c(25:29) ~ '25-29',
      as.numeric(Q1) %in% c(30:34) ~ '30-34',
      as.numeric(Q1) %in% c(35:39) ~ '35-39',
      as.numeric(Q1) %in% c(40:44) ~ '40-44',
      as.numeric(Q1) %in% c(45:49) ~ '45-49',
      as.numeric(Q1) %in% c(50:54) ~ '50-54',
      as.numeric(Q1) %in% c(55:59) ~ '55-59',
      as.numeric(Q1) %in% c(60:64) ~ '60-64',
      as.numeric(Q1) %in% c(65:69) ~ '65-69',
      as.numeric(Q1) >= 70 ~ '70+',
      TRUE ~ NA),
    # pull list experiment into one variable 
    list_treatment = case_when(is.na(`Q14 - version 2`) ~ 0, 
                          TRUE ~ 1),
    list_count = coalesce(`Q14 - version 1`,
                          `Q14 - version 2`),
    # pull framing experiment into one variable
    frame_treatment = case_when(
      `Q15 - Group 1` != 0 ~ "Group 1",
      `Q15 - Group 2` != 0 ~ "Group 2",
      `Q15 - Group 3` != 0 ~ "Group 3",
      `Q15 - Group 4` != 0 ~ "Group 4",
      `Q15 - Group 5` != 0 ~ "Group 5",
      `Q15 - Group 6` != 0 ~ "Group 6",
      `Q15 - Group 7` != 0 ~ "Group 7",
      `Q15 - Group 8` != 0 ~ "Group 8",
      TRUE ~ NA_character_
    )
    ,
    Q15 = coalesce(`Q15 - Group 1`, `Q15 - Group 2`, `Q15 - Group 3`, `Q15 - Group 4`, 
                          `Q15 - Group 5`, `Q15 - Group 6`, `Q15 - Group 7`, `Q15 - Group 8`)
    
  )


# load population frame minus rows containing information on underaged categories and redundant total categories

survey_aug <- read_csv("data/surveys/survey_aug.csv") %>% 
  # adjust education
  filter(gender != "no_answer") %>% 
    mutate(university_education = case_when(
      education %in% uni_education ~ "BA+",
      education %in% na_education ~ "NA",
      TRUE ~ "BA-"),
      age_group = case_when(
        as.numeric(age) %in% c(18:19) ~ '18-19',
        as.numeric(age) %in% c(20:24) ~ '20-24',
        as.numeric(age) %in% c(25:29) ~ '25-29',
        as.numeric(age) %in% c(30:34) ~ '30-34',
        as.numeric(age) %in% c(35:39) ~ '35-39',
        as.numeric(age) %in% c(40:44) ~ '40-44',
        as.numeric(age) %in% c(45:49) ~ '45-49',
        as.numeric(age) %in% c(50:54) ~ '50-54',
        as.numeric(age) %in% c(55:59) ~ '55-59',
        as.numeric(age) %in% c(60:64) ~ '60-64',
        as.numeric(age) %in% c(65:69) ~ '65-69',
        as.numeric(age) >= 70 ~ '70+',
        TRUE ~ NA))

ru_population_frame <- read_csv("data/surveys/ru_population_frame.csv")[-c(1:3,16:18), -c(3,7)]

# harmonise categories
ru_population_frame <- ru_population_frame %>%
  mutate(Age = fct_recode(Age,
                          "35-39" = "35 – 39",
                          "40-44" = "40 – 44",
                          "25-29" = "25 – 29",
                          "45-49" = "45 – 49",
                          "30-34" = "30 – 34",
                          "55-59" = "55 – 59",
                          "50-54" = "50 – 54",
                          "20-24" = "20 – 24",
                          "60-64" = "60 – 64",
                          "18-19" = "18 – 19",
                          "65-69" = "65 – 69",
                          "70+" = "70 и более"),
         Gender = fct_recode(Gender,
                             "Мужской"= "Men",
                             "Женский" = "Women")
  ) %>%
  pivot_longer(
    cols = c("BA+", "BA-", "NA"), 
    names_to = "Education",
    values_to = "Count"
  )

# harmonise features
colnames(ru_population_frame) <- c("gender", "age_group", "university_education",
                                   "Freq")
# 
ru_population_frame[1,4] = 1
ru_population_frame[37,4] = 1

```

## Intro

To create weights, I am working with the 2020
[census data](https://github.com/antndlcrx/nonviolent-repression/blob/main/data/surveys/Tom3_tab1_VPN-2020.xlsx), particulary the cross tabbed gender, age, and university education file [here](https://github.com/antndlcrx/nonviolent-repression/blob/main/data/surveys/ru_population_frame.csv). 

I did not include information about region of residence, even though we could do it after harmonising census data with the survey. 

```{r}
head(ru_population_frame, 5)
```


Note that because in the survey we have a handful of people aged 18-19 who reported having BA education and because "survey" package does not permit 0 in the population frame, I put 1 in Freq for 18-19 men and women BA+ intersection. 

## Sample to Population Comparison


```{r, echo=FALSE, fig.width=20, fig.height=7}
survey_feb_strata <- survey_feb %>% 
  group_by(gender, age_group, university_education) %>% 
  summarise(count = n()) %>%
  mutate(proportion = count / nrow(survey_feb),
         source = "survey_feb")

survey_aug_strata <- survey_aug %>% 
  group_by(gender, age_group, university_education) %>% 
  summarise(count = n()) %>%
  mutate(proportion = count / nrow(survey_feb),
         source = "survey_aug")

pop_strata <- ru_population_frame %>% 
  mutate(proportion = Freq/sum(Freq),
         source = "population")

# combine dfs for plotting
# combined_strata <- rbind(survey_strata, pop_strata)
combined_strata <- combined_strata <- rbind(survey_feb_strata, survey_aug_strata, pop_strata) %>%
  mutate(comparison_group = case_when(
    source == "population" ~ "Population",
    source == "survey_feb" ~ "Survey Feb",
    source == "survey_aug" ~ "Survey Aug",
    TRUE ~ as.character(source)  # Fallback in case there are other sources
  ))

# Plotting
# ggplot(combined_strata, aes(x = university_education, y = proportion, color = source)) +
#   geom_point(aes(shape = source), size = 3) +  # Use shape to differentiate sources
#   geom_line(aes(group = interaction(university_education, source), linetype = source)) +  # Use linetype to differentiate lines
#   facet_grid(gender ~ age_group) +  # Facets based on gender and age_group
#   labs(
#     x = "University Education", 
#     y = "Proportion", 
#     color = "Source",
#     shape = "Source",  # Legend for shapes
#     linetype = "Source"  # Legend for linetypes
#   ) +
#   theme(legend.position = "bottom") + 
#   theme_bw()

# plot differences
ggplot(combined_strata, aes(x = university_education,
                            y = proportion,
                            color = source)) +
  geom_point(size = 3) +
  geom_line(aes(group = interaction(age_group, university_education))) +
  facet_grid(gender ~ age_group) +
  labs(x = "University Education", y = "Proportion", shape = "Source") +
  theme(legend.position = "bottom") +
  theme_bw()



```

The main disparities between Survey Feb and Population are: 

- oversampled young women and undersampled young men, especially age 30-39 for women with university education.
- the opposite for old people. Oversampled older men, undersampled older women without university education.

## Weights witth Survey package

```{r}
## survey library ##
unweighted_data <- svydesign(ids = ~1, data = survey_feb)


weighted <- postStratify(unweighted_data, ~age_group + gender + university_education,
             ru_population_frame, partial=TRUE)

summary(weights(weighted))

```


Note: some stratas had no observations in the survey (NA on education for some age gender groups). This means we had to ignore them in producing weights. 

Also the weights for women with no uni education aged 70+ seem to be too large. It is not surprising given the disparity, but noteworthy. 

```{r, echo=FALSE}
# save weights 
survey_feb$weights <- weights(weighted)


# examine weights
ggplot(survey_feb, aes(x = weights)) +
  geom_histogram(bins = 20, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Weights",
       x = "Weight",
       y = "Frequency")
```


