---
title: "Survey September Analysis"
author: "Maksim Zubok"
date: "2024-10-07"
output: pdf_document
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      results = 'asis')

Sys.getlocale()
# Set this to a locale that supports Cyrillic, for example, on Windows
Sys.setlocale("LC_ALL", "Russian")

##### Set Up #####
pacman::p_load(tidyverse, readr, broom, 
               lubridate, gt, gtsummary, survey, readxl,
               gridExtra, knitr, haven, nnet, stargazer, kableExtra, gplots)
```


```{r}
survey_sept <- read_csv("data/surveys/survey_sept_2024_with_weights.csv",
                        locale = locale(encoding = "UTF-8"))
```



```{r transfrom data}

long_data <- survey_sept %>%
  ### Support protesters actions ###
  rename(age_cat = age_group,
         aggressive = DV1C_1,
          lawabiding = DV1C_2,
          dangerous = DV1C_3,
          trustworthy = DV1C_4,
          think_about_me = DV1C_5,
          is_violent = DV1D_1,
          is_lawabiding = DV1D_2,
          is_lifethreatening = DV1D_3) %>% 
  pivot_longer(
    cols = contains("Group"),  # Dynamically select columns containing "Group"
    names_to = "fact_id",      # New column for the group names
    values_to = "support_protesters_actions"  # New column for the values
  ) %>%
  filter(!is.na(support_protesters_actions)) %>% 
  mutate(
    group_number = as.numeric(sub(".*?([0-9])$", "\\1", fact_id)),  # Extract group numbers,
    protest_type = case_when(
      group_number %in% c(1, 2, 3, 4) ~ "environmental",
      group_number %in% c(5, 6, 7, 8) ~ "political",
    ),
    authorisation = case_when(
      group_number %in% c(6, 5, 2, 1) ~ "authorised",
      group_number %in% c(8, 7, 4, 3) ~ "unauthorised"
    ),
    protest_actions = case_when(
      group_number %% 2 == 1 ~ "demonstration",    # Odd group_numbers represent 'demonstration'
      group_number %% 2 == 0 ~ "clash_with_police" # Even group_numbers represent 'clash_with_police'
    ),
    support_protesters_actions = str_trim(support_protesters_actions),
    support_protesters_numeric = case_when(
      support_protesters_actions == "Oпределенно, не одобряю" ~ 1,
      support_protesters_actions == "Cкорее, не одобряю" ~ 2,
      support_protesters_actions == "Cкорее, одобряю" ~ 3,
      support_protesters_actions == "Определенно, одобряю" ~ 4,
      
      #support_protesters_actions == "Затрудняюсь ответить" ~ 5,
      #support_protesters_actions == "Отказ от ответа" ~ 6,
      TRUE ~ NA_real_ # Turn refuse to NA (no NAs in the data before transformation)
    ),
    ### Support Protesters' Demands ###
    support_protesters_demands = str_trim(DV1A),
    support_protesters_demands_numeric = case_when(
      support_protesters_demands == "Oпределенно, не одобряю" ~ 1,
      support_protesters_demands == "Cкорее, не одобряю" ~ 2,
      support_protesters_demands == "Cкорее, одобряю" ~ 3,
      support_protesters_demands == "Определенно, одобряю" ~ 4,
      
      #support_protesters_demands == "Затрудняюсь ответить" ~ 5,
      #support_protesters_demands == "Отказ от ответа" ~ 6,
      TRUE ~ NA_real_ # Turn refuse to NA (no NAs in the data before transformation)
    ),
    ### Support Arrests ### 
    support_arrests = str_trim(DV1B),
    support_arrests_num = case_when(
    support_arrests == "0 (совершенно не оправданно)" ~ 0,
    support_arrests == "1" ~ 1,
    support_arrests == "2" ~ 2,
    support_arrests == "3" ~ 3,
    support_arrests == "4" ~ 4,
    support_arrests == "5" ~ 5,
    support_arrests == "6" ~ 6,
    support_arrests == "7" ~ 7,
    support_arrests == "8" ~ 8,
    support_arrests == "9" ~ 9,
    support_arrests == "10 (полностью оправданно)" ~ 10,
    # support_arrests == "Затрудняюсь ответить" ~ 11,
    # support_arrests == "Отказ от ответа" ~ 12,
    TRUE ~ NA_real_
  ),
    ### Protesters' Description ###
    across(
    c(aggressive, lawabiding, trustworthy, dangerous, think_about_me),  # List of the variables to transform
    ~ case_when(
      str_trim(.) == "Абсолютно не применимо" ~ 1,
      str_trim(.) == "Скорее не применимо" ~ 2,
      str_trim(.) == "Частично применимо" ~ 3,
      str_trim(.) == "Полностью применимо" ~ 4,
      TRUE ~ NA_real_  # Treat any other response as NA
    ),
    .names = "protesters_are_{col}"  # New variable naming pattern
  ),
    
    ### Protest Description ###
  across(c(is_violent, is_lawabiding, is_lifethreatening),  # List of the variables to transform,
  
    ~ case_when(
      str_trim(.) == "Нет" ~ 1,
      str_trim(.) == "Скорее нет" ~ 2,
      str_trim(.) == "Скорее да" ~ 3,
      str_trim(.) == "Да" ~ 4,
      TRUE ~ NA_real_  # Treat any other response as NA
    )
    )
  ) 

data <- long_data %>% select(c(support_arrests, support_arrests_num, support_protesters_numeric, support_protesters_demands,
                 support_protesters_demands_numeric, protest_type, protest_actions, authorisation, protesters_are_aggressive, protesters_are_lawabiding,
                 protesters_are_trustworthy, protesters_are_think_about_me,
                 protesters_are_dangerous, is_violent, is_lawabiding, is_lifethreatening,
                 weight_manually_calculated))

```

\newpage
## Randomisation Check

```{r randomisation test}
test_rand_type <- glm(factor(protest_type) ~ age + gender + university_education,
                 family=binomial, data=long_data)

test_rand_actions <- glm(factor(protest_actions) ~ age + gender + university_education,
                 family=binomial, data=long_data)

test_rand_authorisation <- glm(factor(authorisation) ~ age + gender + university_education,
                 family=binomial, data=long_data)

# stargazer(test_rand_type,test_rand_actions, test_rand_authorisation,
#           header=FALSE,
#           title="Randomisation Check",
#           digits=2)

summary(test_rand_type)
```

\newpage
## Protest Type Effect on Support of Protesters' Actions

```{r plot means protst type}

ggplot(data, aes(x = support_protesters_numeric, fill = protest_type)) +
  geom_histogram(alpha = 0.5, position = "dodge", bins = 30) +
  labs(title = "Distribution of Support Protesters' Actions by Protest Type",
       x = "Support Protesters Numeric",
       y = "Count") +
  scale_fill_manual(values = c("blue", "red")) + # Customize the colors as needed
  theme_minimal()
```


* The variable "support for protesters' actions" has `r sum(is.na(data$support_protesters_numeric))` missing values. 

```{r env pol case}

# xtabs(~protest_type, data)

```



```{r ttest protst type}
group1 <- data %>%
  filter(protest_type == "environmental") %>%
  pull(support_protesters_numeric)

group2 <- data %>%
  filter(protest_type == "political") %>%
  pull(support_protesters_numeric)

# t.test(group1, group2)
mean(group1, na.rm=T) - mean(group2, na.rm=T)

# m1 <- lm(support_protesters_numeric ~ protest_type, data)
# summary(m1)
```
* The difference between mean support of protesters actions is `r mean(group1, na.rm=T) - mean(group2, na.rm=T)`, which is our effect of interest here.  

```{r plot means type}
plotmeans(formula = support_protesters_numeric ~ protest_type,  # 
             data = data,           # the data frame
             xlab = "Protest type",  # x-axis label
             ylab = "Support for protesters' activities",          # y-axis label
             n.label = T              # (don't) display sample size
 )
```

```{r}
# m1 <- lm(support_protesters_numeric ~ authorisation + protest_type + protest_actions, data = data)
# summary(m1)
```


## Authorisation Effect on Support of Protesters' Demands

```{r plot means authorised}
ggplot(data, aes(x = support_protesters_demands_numeric, fill = authorisation)) +
  geom_histogram(alpha = 0.5, position = "dodge", bins = 30) +
  labs(title = "Distribution of Support Protesters' Demands by Protest Authorisation",
       x = "Support Protesters Numeric",
       y = "Count") +
  scale_fill_manual(values = c("blue", "red")) + # Customize the colors as needed
  theme_minimal()
```


```{r ttest protst authorisation}
group1 <- data %>%
  filter(authorisation == "authorised") %>%
  pull(support_protesters_demands_numeric)

group2 <- data %>%
  filter(authorisation == "unauthorised") %>%
  pull(support_protesters_demands_numeric)

t.test(group1, group2)
mean(group1, na.rm=T) - mean(group2, na.rm=T)

```
* The difference between mean support of protesters actions is `r mean(group1, na.rm=T) - mean(group2, na.rm=T)`, which is our effect of interest here. Difference in means is significantly different from zero. 

```{r plot diff authorisation demands}
plotmeans(formula = support_protesters_demands_numeric ~ authorisation,  # 
             data = data,           # the data frame
             xlab = "Protest type",  # x-axis label
             ylab = "Support for protesters' demands",          # y-axis label
             n.label = T              # (don't) display sample size
 )
```

\newpage
## Interaction Authorisation and Protest Type on Support Arrests

* People are more likely to support arrests of protesters when protests are unauthorised. 
* Effects for political protest and the interaction between political and authorised are not significant. 
* Weighting by population size of key strata (gender x education x age_group) makes protest type significant and increases magnitude of the effects.

```{r}
m_arrests <- lm(support_arrests_num ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)

m_arrests_w <- lm(support_arrests_num ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
# summary(m_arrests)
```


```{r}
stargazer(m_arrests, m_arrests_w,
          header=FALSE,
          title="Arrests are justified",
          digits=2,
          dep.var.labels = c("support arrests", "support arrests (w)"))
```



\newpage
\landscape
## Descriptions of Protesters 
### Unweighted
```{r protesters descriptions}

m_aggressive <- lm(protesters_are_aggressive ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)
m_lawabiding <- lm(protesters_are_lawabiding ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)
m_trustworthy <- lm(protesters_are_trustworthy ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)
m_think_about_me <- lm(protesters_are_think_about_me ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)
m_dangerous <- lm(protesters_are_dangerous ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)
```




```{r display descr protesters results}
models = list(m_aggressive, m_lawabiding, m_trustworthy,m_think_about_me, m_dangerous)

stargazer(models,
          header=FALSE,
          title="Protesters Described As",
          digits=2,
          no.space = TRUE,
          dep.var.labels = c("Aggressive", "Law Abiding", "Trustworthy", "Think about Me",
                             "Dangerous"),
          covariate.labels = c("authorisation (unauthorised)", "type (political)", "actions (demonstation)", "auth x type")
          )

```

\newpage
### Weighted
```{r protesters descriptions w}

m_aggressive <- lm(protesters_are_aggressive ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
m_lawabiding <- lm(protesters_are_lawabiding ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
m_trustworthy <- lm(protesters_are_trustworthy ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
m_think_about_me <- lm(protesters_are_think_about_me ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
m_dangerous <- lm(protesters_are_dangerous ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
```




```{r display descr protesters results w}
models = list(m_aggressive, m_lawabiding, m_trustworthy,m_think_about_me, m_dangerous)

stargazer(models,
          header=FALSE,
          title="Protesters Described As (Weighted)",
          digits=2,
          no.space = TRUE,
          dep.var.labels = c("Aggressive", "Law Abiding", "Trustworthy", "Think about Me",
                             "Dangerous"),
          covariate.labels = c("authorisation (unauthorised)", "type (political)", "actions (demonstation)", "auth x type")
          )

```


\newpage
## Descriptions of Protests
### Unweighted
```{r protest descriptions}

m_violent <- lm(is_violent ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)
m_lawabiding_protest <- lm(is_lawabiding ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)
m_is_lifethreatening <- lm(is_lifethreatening ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data)

```

```{r show results protest descrpn}
models2 = list(m_violent, m_lawabiding_protest, m_is_lifethreatening)

stargazer(models2,
          header=FALSE,
          title="Protest Described As",
          digits=2,
          no.space = TRUE,
          dep.var.labels = c("Violent", "Law-Abiding", "Lifethreatening"),
          covariate.labels = c("authorisation (unauthorised)", "type (political)", "actions (demonstation)", "auth x type")
)
```
\newpage
### Weighted
```{r protest descriptions w}

m_violent <- lm(is_violent ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
m_lawabiding_protest <- lm(is_lawabiding ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)
m_is_lifethreatening <- lm(is_lifethreatening ~ factor(authorisation)*factor(protest_type) + factor(protest_actions), data = data, weights = weight_manually_calculated)

```

```{r show results protest descrpn w}
models2 = list(m_violent, m_lawabiding_protest, m_is_lifethreatening)

stargazer(models2,
          header=FALSE,
          title="Protest Described As (Weighted)",
          digits=2,
          no.space = TRUE,
          dep.var.labels = c("Violent", "Law-Abiding", "Lifethreatening"),
          covariate.labels = c("authorisation (unauthorised)", "type (political)", "actions (demonstation)", "auth x type")
)
```
