---
title: "February Survey Report"
author: "Maksim Zubok"
date: "2024-03-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

Sys.getlocale()
# Set this to a locale that supports Cyrillic, for example, on Windows
Sys.setlocale("LC_ALL", "Russian")

##### Set Up #####
pacman::p_load(tidyverse, readr, broom, 
               lubridate, gt, gtsummary, survey, readxl,
               gridExtra, knitr)


# load survey data
survey_feb <- read_xlsx("data/surveys/survey_feb.xlsx")
# clean data
column_descriptions <- as.character(unlist(survey_feb[1, ]))
names(column_descriptions) <- names(survey_feb)
# example, call: column_descriptions["Q1"]

# remove first row
survey_feb <- survey_feb[-1,]

# categories for education
uni_education <- c("Высшее образование (магистратура)",
                   "Высшее образование (бакалавриат / специалитет)",
                   "Научная степень (кандидат, доктор наук)")

na_education <- c("Затрудняюсь ответить", "Отказ от ответа", "no_answer")

survey_feb <- survey_feb %>%
  mutate(
    gender = as.factor(Q4),
    # adjust dates 
    StartDate = as.POSIXct((as.numeric(StartDate) - 25569) * 86400, origin = "1970-01-01", tz = "UTC"),
    EndDate = as.POSIXct((as.numeric(EndDate) - 25569) * 86400, origin = "1970-01-01", tz = "UTC"),
    RecordedDate = as.POSIXct((as.numeric(RecordedDate) - 25569) * 86400, origin = "1970-01-01", tz = "UTC"),
    # adjust education
    # Q5 %in% na_education ~ "NA" (incude to count NAs)
    university_education = case_when(Q5 %in% uni_education ~ "BA+",
                                     TRUE ~ "BA-"),
    #adjust age
    age_group = case_when(
      as.numeric(Q1) %in% c(18:24) ~ '18-24',
      as.numeric(Q1) %in% c(25:34) ~ '25-34',
      as.numeric(Q1) %in% c(35:44) ~ '35-44',
      as.numeric(Q1) %in% c(45:54) ~ '45-54',
      as.numeric(Q1) %in% c(55:64) ~ '55-64',
      as.numeric(Q1) >= 65 ~ '65+',
      TRUE ~ NA),
    # pull list experiment into one variable 
    list_treatment = case_when(is.na(`Q14 - version 2`) ~ 0, 
                          TRUE ~ 1),
    list_count = coalesce(`Q14 - version 1`,
                          `Q14 - version 2`),
    # pull framing experiment into one variable
    frame_treatment = case_when(
      `Q15 - Group 1` != 0 ~ "Group 1",
      `Q15 - Group 2` != 0 ~ "Group 2",
      `Q15 - Group 3` != 0 ~ "Group 3",
      `Q15 - Group 4` != 0 ~ "Group 4",
      `Q15 - Group 5` != 0 ~ "Group 5",
      `Q15 - Group 6` != 0 ~ "Group 6",
      `Q15 - Group 7` != 0 ~ "Group 7",
      `Q15 - Group 8` != 0 ~ "Group 8",
      TRUE ~ NA_character_
    )
    ,
    Q15 = coalesce(`Q15 - Group 1`, `Q15 - Group 2`, `Q15 - Group 3`, `Q15 - Group 4`, 
                          `Q15 - Group 5`, `Q15 - Group 6`, `Q15 - Group 7`, `Q15 - Group 8`)
    
  )


# load population frame minus rows containing information on underaged categories and redundant total categories

survey_aug <- read_csv("data/surveys/survey_aug.csv",
                       locale = locale(encoding = "UTF-8")) %>% 
  # adjust education
  # education %in% na_education ~ "NA"
  filter(gender != "no_answer") %>% 
    mutate(university_education = case_when(
      education %in% uni_education ~ "BA+",
      TRUE ~ "BA-")
    )
# -c(1:3,16:18) 
ru_population_frame <- read_csv("data/surveys/ru_population_frame.csv")[-c(1:3,16:18), -c(3,7)]

# Define wider age categories
wider_age_categories <- list(
  '18-24' = c('18 – 19', '20 – 24'),
  '25-34' = c('25 – 29', '30 – 34'),
  '35-44' = c('35 – 39', '40 – 44'),
  '45-54' = c('45 – 49', '50 – 54'),
  '55-64' = c('55 – 59', '60 – 64'),
  '65+' = c('65 – 69', '70 – 74', '75 – 79', '80 – 84', '85+')
)

# Function to collapse age categories
collapse_age_categories <- function(df, age_mapping) {
  df %>%
    mutate(Age = factor(Age, levels = unlist(age_mapping))) %>%
    rowwise() %>%
    mutate(Age = list(names(age_mapping)[sapply(age_mapping, \(x) Age %in% x)])) %>%
    group_by(Gender, Age) %>%
    summarize(across(c(`BA+`, `BA-`, `NA`), sum, na.rm = TRUE), .groups = 'drop')
}

# Apply the function
collapsed_df <- collapse_age_categories(ru_population_frame, wider_age_categories)


# harmonise categories
ru_population_frame <- collapsed_df %>%
  mutate(Gender = fct_recode(Gender,
                             "Мужской"= "Men",
                             "Женский" = "Women")
  ) %>%
  pivot_longer(
    cols = c("BA+", "BA-", "NA"), 
    names_to = "Education",
    values_to = "Count"
  )

# harmonise features
colnames(ru_population_frame) <- c("gender", "age_group", "university_education",
                                   "Freq")


```

## Intro

To create weights, I am working with the 2020
[census data](https://github.com/antndlcrx/nonviolent-repression/blob/main/data/surveys/Tom3_tab1_VPN-2020.xlsx), particulary the cross tabbed gender, age, and university education file [here](https://github.com/antndlcrx/nonviolent-repression/blob/main/data/surveys/ru_population_frame.csv). 

I did not include information about region of residence, even though we could do it after harmonising census data with the survey. 

```{r}
head(ru_population_frame, 5)
```


Note that because in the survey we have a handful of people aged 18-19 who reported having BA education and because "survey" package does not permit 0 in the population frame, I put 1 in Freq for 18-19 men and women BA+ intersection. 

## Sample to Population Comparison


```{r, echo=FALSE, warning=FALSE, fig.width=20, fig.height=7}
survey_feb_strata <- survey_feb %>% 
  group_by(gender, age_group, university_education) %>% 
  summarise(count = n()) %>%
  mutate(proportion = count / nrow(survey_feb),
         source = "survey_feb")

survey_aug_strata <- survey_aug %>% 
  group_by(gender, age_group, university_education) %>% 
  summarise(count = n()) %>%
  mutate(proportion = count / nrow(survey_feb),
         source = "survey_aug")

pop_strata <- ru_population_frame %>% 
  mutate(proportion = Freq/sum(Freq),
         source = "population")

# combine dfs for plotting
# combined_strata <- rbind(survey_strata, pop_strata)
combined_strata <- combined_strata <- rbind(survey_feb_strata, survey_aug_strata, pop_strata) %>%
  mutate(comparison_group = case_when(
    source == "population" ~ "Population",
    source == "survey_feb" ~ "Survey Feb",
    source == "survey_aug" ~ "Survey Aug",
    TRUE ~ as.character(source)  # Fallback in case there are other sources
  ))

# Plotting
# ggplot(combined_strata, aes(x = university_education, y = proportion, color = source)) +
#   geom_point(aes(shape = source), size = 3) +  # Use shape to differentiate sources
#   geom_line(aes(group = interaction(university_education, source), linetype = source)) +  # Use linetype to differentiate lines
#   facet_grid(gender ~ age_group) +  # Facets based on gender and age_group
#   labs(
#     x = "University Education", 
#     y = "Proportion", 
#     color = "Source",
#     shape = "Source",  # Legend for shapes
#     linetype = "Source"  # Legend for linetypes
#   ) +
#   theme(legend.position = "bottom") + 
#   theme_bw()

# plot differences
ggplot(combined_strata, aes(x = university_education,
                            y = proportion,
                            color = source)) +
  geom_point(aes(shape = source), size = 3) +
  geom_line(aes(group = interaction(age_group, university_education))) +
  facet_grid(gender ~ age_group) +
  labs(x = "University Education", y = "Proportion", shape = "Source") +
  theme(legend.position = "bottom") +
  theme_bw()



```

The main disparities between Survey Feb and Population are: 

- oversampled young women and undersampled young men, especially age 30-39 for women with university education.
- the opposite for old people. Oversampled older men, undersampled older women without university education.

## Weights witth Survey package

To compute post-stratification weights we rely on the `postStratify` function from the `survey` package. The function adjusts the sampling and replicate weights so that the joint distribution of a set of
post-stratifying variables matches the known population joint distribution. **However, the package documentation does not describe how exactly the adjustment is implemented.**

```{r warning=FALSE}
## survey library ##
unweighted_data <- svydesign(ids = ~1, data = survey_feb)


weighted <- postStratify(unweighted_data, ~age_group + gender + university_education,
             ru_population_frame, partial=TRUE)

# save weights 
survey_feb$weight <- weights(weighted)
sum_feb <- summary(weights(weighted))
sum_feb
```
Note: some strata had no observations in the survey (NA on education for some age gender groups). This means we had to ignore them in producing weights. 

Also the weights for women with no uni education aged 70+ seem to be too large. It is not surprising given the disparity, but noteworthy.

```{r warning=FALSE}
## survey library ##
unweighted_data <- svydesign(ids = ~1, data = survey_aug)


weighted <- postStratify(unweighted_data, ~age_group + gender + university_education,
             ru_population_frame, partial=TRUE)

# save weights 
survey_aug$weight <- weights(weighted)
sum_aug <- summary(weights(weighted))
sum_aug
```

For August, we also see that some weights are much larger than others. As you can see in the graphs below, the distribution of weights is similarly skewed and the disparities between the bulk of the distribution and its tales are in the same orders of magnitude. However, the largest weight in Feb survey is three times bigger than the largest weight in Aug survey. 

The largest weights in both surveys relate to different population groups.


```{r echo=FALSE}
top_five_rows_feb <- survey_feb %>%
  arrange(desc(weight)) %>% 
  select(age_group, gender, university_education, weight) %>% 
  head(5)

kable(top_five_rows_feb, caption = "February Survey, Top Five Rows by Weight", align = 'c')

```

```{r echo=FALSE}
top_five_rows_aug <- survey_aug %>%
  arrange(desc(weight)) %>% 
  select(age_group, gender, university_education, weight)%>% 
  head(5)

kable(top_five_rows_aug, caption = "August Survey, Top Five Rows by Weight", align = 'c')
```


```{r, echo=FALSE}

survey_feb_selected <- survey_feb %>%
  mutate(Survey = 'February') %>%
  select(weight, Survey)

survey_aug_selected <- survey_aug %>%
  mutate(Survey = 'August') %>%
  select(weight, Survey)

combined_weights <- rbind(survey_feb_selected, survey_aug_selected)

ggplot(combined_weights, aes(x = weight, fill = Survey)) +
  geom_histogram(data = subset(combined_weights, Survey == 'February'), bins = 100, alpha = 0.5, color = "black") +
  geom_histogram(data = subset(combined_weights, Survey == 'August'), bins = 100, alpha = 0.5, color = "black") +
  scale_fill_manual(values = c("February" = "blue", "August" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Weights by Survey",
       x = "Weight",
       y = "Frequency")


```

```{r echo=FALSE}
plot_feb <- ggplot(survey_feb_selected, aes(x = weight)) +
  geom_histogram(bins = 100, fill = "blue", color = "black", alpha = 0.5) +
  theme_minimal() +
  labs(title = "February Survey: Distribution of Weights",
       x = "Weight",
       y = "Frequency")

plot_aug <- ggplot(survey_aug_selected, aes(x = weight)) +
  geom_histogram(bins = 100, fill = "red", color = "black", alpha = 0.5) +
  theme_minimal() +
  labs(title = "August Survey: Distribution of Weights",
       x = "Weight",
       y = "Frequency")

grid.arrange(plot_feb, plot_aug, ncol = 2)
```


## Weights created manually
To check the plausibility of resulting weights, we create alternative weights based on the population frequencies of the combination of the same strata (Yana's approach). The weights are calculated for each category:
\[ \text{weight}_i = \frac{\text{population frequency}_i}{\text{sample frequency}_i} \]


```{r include=FALSE}
# revert back the changes from above
ru_population_frame <- read_csv("data/surveys/ru_population_frame.csv")[-c(1:3,16:18), -c(3,7)]

# harmonise categories
ru_population_frame <- ru_population_frame %>%
  mutate(Age = fct_recode(Age,
                          "35-39" = "35 – 39",
                          "40-44" = "40 – 44",
                          "25-29" = "25 – 29",
                          "45-49" = "45 – 49",
                          "30-34" = "30 – 34",
                          "55-59" = "55 – 59",
                          "50-54" = "50 – 54",
                          "20-24" = "20 – 24",
                          "60-64" = "60 – 64",
                          "18-19" = "18 – 19",
                          "65-69" = "65 – 69",
                          "70+" = "70 и более"),
         Gender = fct_recode(Gender,
                             "Мужской"= "Men",
                             "Женский" = "Women")
  ) %>%
  pivot_longer(
    cols = c("BA+", "BA-", "NA"), 
    names_to = "Education",
    values_to = "Count"
  )

# harmonise features
colnames(ru_population_frame) <- c("gender", "age_group", "university_education",
                                   "Freq")
```


```{r }
# calculate weights and print the df with weights
weights_aug_strata <- left_join(survey_aug_strata,
                            pop_strata,
                            c("gender", "age_group", "university_education")) %>% 
  rename(population_proportion = proportion.y,
         sample_proportion = proportion.x)  %>% 
  # calculate weights as popul prop/sample prop
  mutate(weight = population_proportion / sample_proportion)

sum_man_aug <-summary(weights_aug_strata$weight)
sum_man_aug
```


```{r }
# calculate weights and print the df with weights
weights_feb_strata <- left_join(survey_feb_strata,
                            pop_strata,
                            c("gender", "age_group", "university_education")) %>% 
  rename(population_proportion = proportion.y,
         sample_proportion = proportion.x)  %>% 
  # calculate weights as popul prop/sample prop
  mutate(weight = population_proportion / sample_proportion)

# head(weights_feb_strata)
sum_man_feb <- summary(weights_feb_strata$weight)
sum_man_feb
```

```{r echo=FALSE}

weights_feb_strata <- weights_feb_strata %>%
  mutate(Survey = 'February') %>%
  select(weight, Survey)

weights_aug_strata <- weights_aug_strata %>%
  mutate(Survey = 'August') %>%
  select(weight, Survey)

combined_weights <- rbind(weights_feb_strata, weights_aug_strata)

ggplot(combined_weights, aes(x = weight, fill = Survey)) +
  geom_histogram(data = subset(combined_weights, Survey == 'February'), bins = 100, alpha = 0.5, color = "black") +
  geom_histogram(data = subset(combined_weights, Survey == 'August'), bins = 100, alpha = 0.5, color = "black") +
  scale_fill_manual(values = c("February" = "blue", "August" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Weights by Survey",
       x = "Weight",
       y = "Frequency")


```

```{r echo=FALSE, warning=FALSE}
plot_feb <- ggplot(weights_feb_strata, aes(x = weight)) +
  geom_histogram(bins = 100, fill = "blue", color = "black", alpha = 0.5) +
  theme_minimal() +
  labs(title = "February: Distribution of Weights",
       x = "Weight",
       y = "Frequency")

plot_aug <- ggplot(weights_aug_strata, aes(x = weight)) +
  geom_histogram(bins = 100, fill = "red", color = "black", alpha = 0.5) +
  theme_minimal() +
  labs(title = "August: Distribution of Weights",
       x = "Weight",
       y = "Frequency")

grid.arrange(plot_feb, plot_aug, ncol = 2)
```

Calculating weights this way gives us the same overall picture. The main difference is in the orders of magnitude between the median weight and the tail (highest weight). 

For **February** survey, the difference (max weight / median weight) with `postStratify` is **`r round(sum_feb["Max."] / sum_feb["Median"], 2)`**, but with simple manually created weights it is **`r round(sum_man_feb["Max."] / sum_man_feb["Median"], 2)`**. For **August** survey, the difference with `postStratify` is **`r round(sum_aug["Max."] / sum_aug["Median"], 2)`**, but with simple manually created weights it is **`r round(sum_man_aug["Max."] / sum_man_aug["Median"], 2)`**.

Note that some observations in February survey have a weight of zero because they do not exist in the population census. These are women 18-19 years old with university education. My suspicion on why we have these observations is that some respondents might have misreported their education attainment. 

