---
title: "Results Weighted"
author: "Maksim Zubok"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
header-includes:
- \usepackage{pdflscape}
- \usepackage{geometry}
- \usepackage{longtable}
- \geometry{a4paper, margin=1in}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: 
  pdf_document:
    latex_engine: lualatex
    toc: True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      results='asis')


pacman::p_load(rio, tidyverse, readr, broom, 
               lubridate, gt, gtsummary, survey, readxl,
               gridExtra, knitr, haven, stargazer, nnet, ggeffects)

DATA_CODES = "https://cdn.githubraw.com/antndlcrx/nonviolent-repression/main/data/acled_raw_data/region_codes.xlsx"

acled <- import("C:/Users/murrn/GitHub/nonviolent-repression/data/acled_processed_data/acled_with_org_indicator.csv") 

codes = data <- openxlsx::read.xlsx(DATA_CODES, sheet = "Sheet1")
codes <- codes %>%
  mutate(region_name_en = str_trim(region_name_en))


## unique observations 

length(unique(acled$notes))
# Finding duplicate observations in 'variable'
duplicates <- duplicated(acled$notes)

# Getting the row IDs of these duplicates
row_ids <- which(duplicates)

# Print events
acled$notes[row_ids]
acled_clean <- acled[!duplicated(acled$notes), ]

acled_clean <- acled_clean %>% 
  mutate(
    date = ymd(as.character(event_date)),
    month_year = as.Date(paste0(month_year, "-01"))
    )

# Convert date column to Date object and create DVs:
# pre/post invasion
# election_month
acled_clean <- acled_clean %>% 
  mutate(date = ymd(event_date),
         pred_labels = recode(pred_labels,
                              "war (pro)" = "war_pro",
                              "war (anti)" = "war_anti"),
         month_year = format(date, "%Y-%m"),
         post_invasion = factor(case_when(
    date >= as.Date("2022-02-24") ~ 1,
    TRUE ~ 0)),
    police_violence = factor(case_when(
    sub_event_type %in% c("Protest with intervention", "Excessive force against protesters") ~ 1,
    TRUE ~ 0
  )),
    election_month = factor(case_when(
           month_year %in% c("2021-09", "2018-03", "2024-03", "2020-06", "2020-07") ~ 1,
           TRUE ~ 0))
    )


mapping <- c(
  'Saint Petersburg' = 'The City of Saint-Petersburg',
  'Sverdlovsk' = 'Sverdlovsk region',
  'Moscow' = 'The City of Moscow',
  'Republic of Tatarstan' = 'Republic of Tatarstan',
  'Novosibirsk' = 'Novosibirsk region',
  'Novgorod' = 'Novgorod region',
  'Samara' = 'Samara region',
  'Republic of Mari El' = 'Republic of Mariy El',
  'Republic of Dagestan' = 'Republic of Daghestan',
  'Tomsk' = 'Tomsk region',
  'Republic of Karachay-Cherkessia' = 'Karachaev-Circassian Republic',
  'Moscow Oblast' = 'Moscow region',
  'Volgograd' = 'Volgograd region',
  'Chelyabinsk' = 'Chelyabinsk region',
  'Kaliningrad' = 'Kaliningrad region',
  'Khabarovsk' = 'Khabarovsk territory',
  'Republic of Khakassia' = 'Republic of Khakassia',
  'Perm' = 'Perm region',
  'Vologda' = 'Vologda region',
  'Republic of Sakha' = 'Republic of Sakha (Yakutia)',
  'Tula' = 'Tula region',
  'Kemerovo' = 'Kemerovo region',
  'Altai' = 'Altai territory',
  'Republic of Bashkortostan' = 'Republic of Bashkortastan',
  'Penza' = 'Penza region',
  'Republic of Chuvash' = 'Chuvash Republic',
  'Krasnoyarsk' = 'Krasnoyarsk territory',
  'Orenburg' = 'Orenburg region',
  'Tyumen' = 'Tyumen region',
  'Republic of Kabardino-Balkaria' = 'Kabardian-Balkar Republic',
  'Kostroma' = 'Kostroma region',
  'Vladimir' = 'Vladimir region',
  'Arkhangelsk' = 'Arkhangelsk region',
  'Rostov' = 'Rostov region',
  'Krasnodar' = 'Krasnodar territory',
  'Khanty-Mansi' = 'Khanty-Mansi autonomous',
  'Kaluga' = 'Kaluga region',
  'Republic of Karelia' = 'Republic of Karelia',
  'Voronezh' = 'Voronezh region',
  'Ryazan' = 'Ryazan region',
  'Zabaykalskiy' = 'Chita region',
  'Ulyanovsk' = 'Ulyanovsk region',
  'Republic of Komi' = 'Republic of Komi',
  'Republic of Buryatia' = 'Republic of Buryatia',
  'Nizhny Novgorod' = 'Nizhny novgorod region',
  'Ivanovo' = 'Ivanovo region',
  'Saratov' = 'Saratov region',
  'Irkutsk' = 'Irkutsk region',
  'Republic of Altai' = 'Republic of Altai',
  'Primorskiy' = 'Primorsky territory',
  'Republic of Chechnya' = 'Chechen Republic',
  'Belgorod' = 'Belgorod region',
  'Lipetsk' = 'Lipetsk region',
  'Udmurt Republic' = 'Udmurt Republic',
  'Astrakhan' = 'Astrakhan region',
  'Kirov' = 'Kirov region',
  'Yaroslavl' = 'Yaroslavl region',
  'Kursk' = 'Kursk region',
  'Omsk' = 'Omsk region',
  'Republic of Mordovia' = 'Republic of Mordovia',
  'Tambov' = 'Tambov region',
  'Smolensk' = 'Smolensk region',
  'Republic of Ingushetia' = 'Republic of Ingushetia',
  'Oryol' = 'Oryol region',
  'Pskov' = 'Pskov region',
  'Republic of Tuva' = 'Republic of Tyva',
  'Republic of North Ossetia-Alania' = 'Republic of North Ossetia -Alania',
  'Jewish Autonomous Oblast' = 'Jewish autonomous region',
  'Kamchatka' = 'Kamchatka region',
  'Magadan' = 'Magadan region',
  'Republic of Kalmykia' = 'Republic of Kalmykia',
  'Yamalo-Nenets' = 'Yamalo-Nenets autonomous',
  'Bryansk' = 'Bryansk region',
  'Stavropol' = 'Stavropol territory',
  'Tver' = 'Tver region',
  'Murmansk' = 'Murmansk region',
  'Republic of Adygea' = 'Republic of Adygeya',
  'Amur' = 'Amur region',
  'Sakhalin' = 'Sakhalin region',
  'Leningrad' = 'Leningrad region',
  'Chukotka' = 'Chukotka autonomous area',
  'Nenets' = 'Nenets autonomous area',
  'Kurgan' = 'Kurgan region'
)


# apply mapping
acled_clean$admin1 <- mapping[acled_clean$admin1]

# create dummies for protest types
acled_clean_dummy <- acled_clean %>%
  mutate(pred_labels = factor(pred_labels)) %>%
  mutate(dummy = 1) %>%
  pivot_wider(names_from = pred_labels, values_from = dummy, values_fill = list(dummy = 0)) %>% 
  mutate(non_pol = factor(case_when(political == 1 ~ 0,
                             TRUE ~ 1)))

```



```{r base regressions}
#### Political and Other protests with controls ####


# pol_base <- lm(political ~ post_invasion, acled_clean_dummy)
pol_base <- glm(political ~ post_invasion  + month_year, data = acled_clean_dummy, family = binomial)
nonpol_base <- glm(non_pol ~ post_invasion + month_year, data = acled_clean_dummy, family = binomial)

pol_controls <- glm(political ~ post_invasion + election_month + month_year + admin1, data = acled_clean_dummy, family = binomial)
nonpol_controls <- glm(non_pol ~ post_invasion + election_month + month_year + admin1, data = acled_clean_dummy, family = binomial)

# summary(pol_base)
```

```{r base excl war protest}

#### Other protests with controls excluded war protests ####

acled_clean_dummy_no_war <- acled_clean_dummy %>% 
  mutate() %>% 
  filter(!(war_pro == 1 | war_anti == 1))

# nonpol_subset_nowar <- lm(non_pol ~ post_invasion, acled_clean_dummy_no_war)
nonpol_nowar <- glm(non_pol ~ post_invasion + month_year, data = acled_clean_dummy_no_war, family = binomial)
nonpol_nowar_controls <- glm(non_pol ~ post_invasion + election_month + month_year + admin1, data = acled_clean_dummy_no_war, family = binomial)

# summary(nonpol_subset_nowar)

```

# Protest Log Odds with and without War Protest

```{r create reg table one}
models = list(pol_base, pol_controls, 
          nonpol_base, nonpol_controls, nonpol_nowar,
          nonpol_nowar_controls)

stargazer(models,
          digits=2,
          header=FALSE,
          no.space = TRUE, # to remove the spaces after each 
          column.sep.width = "2pt", # to reduce column width
          font.size = "small", # to make font size smaller
          dep.var.labels=c("Political Protest", "Other Protest"),
          covariate.labels=c("Post Invasion", "Election Month"),

          title="Log Odds of Protest",
          notes = '',
  notes.append = TRUE,
  notes.align = 'l',
  omit = c("year", "admin"),
  add.lines = list(c('Month-Year FE','Yes','Yes','Yes', 'Yes', 'Yes', 'Yes'),
                   c('War Protests Excluded', 'No', 'No', 'No', 'No', 'Yes', 'Yes'),
                   c('Region FE', 'No', "Yes", "No", "Yes", "No", "Yes")
                   )
          )
```


```{r multinom reg, echo = FALSE, warning = FALSE, message = FALSE, results=FALSE}

#### Protest Organised by Kreml/Syst/Other actors ####

m_log <- multinom(org_indicator ~ post_invasion + month_year, data = acled_clean_dummy)

m_log_controls <- multinom(org_indicator ~  post_invasion + election_month + month_year + admin1, data = acled_clean_dummy)
```


\newpage
# Protest by Organiser


In the table below, we depict how the invasion has affected the propensity of different actors to organise a protest. We distinguish three actor categories: pro-Kremlin actors, systemic opposition actors, and other actors.

\begin{center}
\begin{longtable}{|p{0.5\textwidth}|p{0.5\textwidth}|}
\hline
\textbf{Pro-Kremlin} & \textbf{Systemic Opposition} \\
\hline
\endfirsthead
\hline
\textbf{Pro-Kremlin} & \textbf{Systemic Opposition} \\
\hline
\endhead
ER: United Russia & CP: A Just Russia \\
Former Government of Russia (2000-) & KPRF: Communist Party of the Russian Federation \\
Former Military Forces of Russia (2000-) & KR: Communists of Russia \\
Former Police Forces of Russia (2000-) & LDPR: Liberal Democratic Party of Russia \\
Government of Russia (2000-) Republic of Chechnya & New People \\
Military Forces of Russia (2000-) & PR: Party of Growth \\
Military Forces of Russia (2000-) National Guard - Special Purpose Police Unit & Yabloko: Russian United Democratic Party \\
Motherland Party & \\
NOD: National Liberation Movement & \\
NPSR: National Patriotic Forces of Russia & \\
NPSR: People's Patriotic Union of Russia & \\
Police Forces of Russia (2000-) & \\
VVPOD: Young Army Cadets National Movement & \\
Zakhar Prilepin's Guard & \\
\hline
\end{longtable}
\end{center}


```{r create reg table two}
stargazer(m_log, m_log_controls,
          digits=2,
          header=FALSE,
          no.space = TRUE, # to remove the spaces after each 
          column.sep.width = "2pt", # to reduce column width
          font.size = "small", # to make font size smaller
          dep.var.labels=c("Other", "Pro Kremlin", "Systemic Opposition", "Other", "Pro Kremlin", "Systemic Opposition"),
          covariate.labels=c("Post Invasion", "Election Month"),

          title="Log Odds of Protest by Protest Organiser",
          notes = '',
  notes.append = TRUE,
  notes.align = 'l',
  omit = c("year", "admin"),
  add.lines = list(c('Month-Year FE','Yes','Yes', 'Yes','Yes','Yes','Yes'),
                   c('War Protests Excluded', 'No', 'No','No', 'No','No', 'No'),
                   c('Region FE', 'No','No', 'No', "Yes", 'Yes','Yes')
                   )
          )

```

\newpage

# Protest met with Violence

Next, we look at protests that were met with police violence. To identify them, we rely on acled classification of protest event subtype and define events which acled labeled as "Protest with intervention" or "Excessive force against protesters" as protests met with police violence. 

Protest type variable here is coded 1 for "non-political" and 0 for "political".

```{r regs on repression}

# pol_base <- lm(political ~ post_invasion, acled_clean_dummy)
# violnce_base <- glm(police_violence ~ political + month_year, data = acled_clean_dummy, family = binomial)
# violnce_controls <- glm(police_violence ~ political + election_month + month_year + admin1, data = acled_clean_dummy, family = binomial)


nonpol_violnce_base <- glm(police_violence ~ non_pol + month_year, data = acled_clean_dummy, family = binomial)

nonpol_violnce_controls <- glm(police_violence ~ non_pol + election_month + month_year + admin1, data = acled_clean_dummy, family = binomial)

nonpol_violnce_controls_war <- glm(police_violence ~ non_pol + election_month + post_invasion + month_year + admin1, data = acled_clean_dummy, family = binomial)

nonpol_violnce_controls_int <- glm(police_violence ~ non_pol + election_month + non_pol* post_invasion + month_year + admin1, data = acled_clean_dummy, family = binomial)


```



```{r reg table violence}
models_violence = list(nonpol_violnce_base, 
          nonpol_violnce_controls, nonpol_violnce_controls_war, nonpol_violnce_controls_int)

stargazer(models_violence,
          digits=2,
          header=FALSE,
          no.space = TRUE, # to remove the spaces after each 
          column.sep.width = "2pt", # to reduce column width
          font.size = "small", # to make font size smaller
          dep.var.labels=c("Protest Met with Violence"),
          covariate.labels=c("Protest Type",  "Election Month", "Post Invasion",
                             "Post Invasion * Protest Type"),

          title="Log Odds of Protest met with Police Violence",
          notes = '',
  notes.append = TRUE,
  notes.align = 'l',
  omit = c("year", "admin"),
  add.lines = list(c('Month-Year FE','Yes','Yes','Yes', 'Yes'),
                   c('War Protests Excluded', 'No', 'No', 'No', 'No'),
                   c('Region FE', "No", "Yes", "Yes", "Yes")
                   )
          )


```

\newpage
The figure below depicts the 

```{r}
ggpredict(nonpol_violnce_controls_int, c("post_invasion", "non_pol")) %>% plot()
```

